### 2017-10-25 Draft2/Appending.Dynamic.tex
Lists

\begin{description}
	\item[initial capacity] The capacity of a dynamic a array when one item is appended to it. I denote this $\VarInitCapacity$.\\
	(The capacity of any dynamic array with size zero should be zero.)
	\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ grows. I denote this with $\VarGrowthFactor$.
\end{description}

>>>>

\begin{description}
	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of a dynamic a array when one item is appended to it.\\
	(The capacity of any dynamic array with size zero should be zero.)
	\item[growth factor] Denoted by $\VarGrowthFactor$. The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ grows.
\end{description}
